---
title: "Regrssion models - Course Project"
author: "Fabrice Tereszkiewciz"
date: "16 Oct 2015"
output: html_document
---

```{r global_options, include=FALSE}
library(knitr)
read_chunk('./project.R')
knitr::opts_chunk$set(warning=FALSE, message=FALSE)
```

```{r, include=FALSE}
<<loadPackages>>
<<loadData>>
```

## Introduction

You work for Motor Trend, a magazine about the automobile industry. Looking at a data set of a collection of cars, they are interested in exploring the relationship between a set of variables and miles per gallon (MPG) (outcome). They are particularly interested in the following two questions.

## Executive summary


## Exploratory Analysis

Let's look at a simple plot to see the difference in MPG per transmission type.

```{r}
<<exploAnalysis>>
```

The dataset contains 32 observations and 11 variables. 

We can have a quick look at the MPG values by transmission type.

```{r, fig.height=4, fig.align='center'}
<<exploplot>>
g
```

It looks like manual transmission increases the MPG value. 

## Regression

We can try a marginal linear regression first to see the effect of the transmission type on MPG, holding all other variables constant.

```{r}
<<MTlm>>
```

We can see that on average manual transmission vehicules can do 7.245 miles per gallon more than automatic transmission vehicules. Looking at the R-squared error, we can see that only `r round(summary(mdl.mar)$r.squared * 100, 2)`% of the variance in MPG is explained by the type of transmission. We must therefore look at other variables in order to explain the MPG change.

We can do a step search to find the most optimal model to fit the MPG value.

```{r, results="hide"}
<<stepSearch>>
```
```{r}
summary(mdl.opt)
```

So we can explain the MPG better if we also include the weight (`wt`), horse power (`hp`), and cylinder 16 and 8 (`cyl16`, `cyl18`) to our model. We can now say that a manual transmission increases the MPG by 1.81 holding all other variables constant.

```{r}
anova(mdl.mar, mdl.opt)
```

Here we can see that the P value is highly significant, which confirms that the model `mdl.opt` is more accurate than the marginal model `mdl.mar`.

## Residuals and Diagnostics

The plot is in appendix.

- the points and the line show no signs of correlation on the Residuals vs. Fitted plot.
- the poitns follow the line on the Normal Q-Q plot, so we can assume the residuals are normally distributed.
- the points are randomly distributed on the Scale-Location, so we can assume constant variance.
- all the points are within the 0.5 bands of the Cook's disctance (NEED TO PLOT THIS !!).

## Inference

A simple t-test shows that the transmission is an important parameter.

```{r}
t.test(mpg ~ am, data = mtcars)
```

As the 95% interval doesn't contain 0, we can not reject the hypothesis that the transmission is not important.

# Appendix

## Models diagnostic

```{r, fig.width=10, fig.height=8}
<<plotDiagModelOptimal>>
```